---
title: 'Interconnected Environmental Challenges: CO₂ Emissions, Renewable Energy, and Air Pollution in the Context of UN Sustainability Goals'
author: "Jessie Gao, Lu Liu, Chunyi Xu, and Lauren Xu" 
date: "Spring 2025"
output: pdf_document
toc: true
---

\newpage
\tableofcontents 
\newpage
\listoftables 
\newpage
\listoffigures 
\newpage

```{r project.setup, message=FALSE, warning=FALSE, error=FALSE, results='hide'}
knitr::opts_chunk$set(echo = TRUE)
# Set your working directory
library (here)
##Checking working directory is the project folder
here()

# Load your packages
library(readxl)
library (ggplot2)
library(tidyverse)
library (lubridate)
library(dplyr)
library(writexl)


# Set your ggplot theme
my.default.theme <- theme_classic(base_size = 15) +
  theme(plot.background = element_rect(color='white',fill='white'),
        plot.title = element_text(color='black', size = 15),
        axis.text = element_text(color = 'black',size = 10), 
        panel.grid.minor = element_line(size = 0.5),
        panel.grid.major = element_line(size = 0.5),
        legend.background = element_rect(color='white', fill = 'white'),
        legend.position = "right",
        legend.title = element_text(color='black',size=10),
        legend.text = element_text(size = 10))

#Setting the theme as the default theme
theme_set(my.default.theme)

# Load your datasets
Sus_Env <- read_excel("/Users/xuchunyi/Desktop/GaoLuXuXu_ENV872_EDA_FinalProject/GaoLuXuXu_ENV872_EDA_FinalProject/Raw_Data/Sus_Env.xlsx")

#Viewing the structure of the dataset
dim (Sus_Env)
view(Sus_Env)
colnames(Sus_Env)

# Data Wrangling
##Removing unnecessary rows and replacing missing values with N/A
Sus_Env_Step1 <- Sus_Env %>% 
  na.omit() %>%
  mutate(`2020` = na_if(`2020`, '..'))  

##Changing the year column to character
Sus_Env_Step1 <- Sus_Env_Step1 %>%
  mutate(across(4:ncol(Sus_Env_Step1), as.character))

##Reorganizing the dataset and filtering Series Name to keep variables of interest (PM, CO2, and Renew)
Sus_Env_Processed <- Sus_Env_Step1 %>%
  pivot_longer(cols = -c("Country Code", "Country Name", "Series Name"), 
               names_to = "Year",      
               values_to = "Value") %>%
  filter(`Series Name` %in% c("PM", "CO2", "Renew"))


##Checking the class of the variable Value, and the result is character
class (Sus_Env_Processed$Value)

##Converting the Value to a numeric variable
Sus_Env_Processed <- Sus_Env_Processed %>%
  mutate(Value = as.numeric(Value))

##Checking the class of the variable Value, and the result is numeric
class (Sus_Env_Processed$Value)

#Saving the processed dataset
output_file <- "/Users/xuchunyi/Desktop/GaoLuXuXu_ENV872_EDA_FinalProject/GaoLuXuXu_ENV872_EDA_FinalProject/Processed_Data/Sus_Env_Processed.xlsx"
write_xlsx(Sus_Env_Processed, path = output_file)

```


# Rationale and Research Questions
The global climate crisis has intensified over the past decade, with rising temperatures, air pollution, and energy insecurity threatening the health and stability of communities worldwide. Carbon dioxide (CO₂) emissions from fossil fuel combustion are a primary driver of climate change, while exposure to fine particulate matter (PM2.5) has been strongly linked to adverse health outcomes such as respiratory and cardiovascular disease. Meanwhile, the transition to renewable energy represents a critical pathway for reducing both greenhouse gas emissions and harmful air pollutants. Given the importance of environmental indicators in evaluating national progress toward sustainability, this study aims to explore the interplay between CO₂ emissions, PM2.5 pollution, and renewable energy adoption in the context of global development goals. 

We selected data from the World Bank’s World Development Indicators, which offer a reliable, standardized, and accessible source for cross-country comparisons. The four countries in our study, which are Germany, the United States, China, and Colombia, were chosen to provide a balanced perspective between developed and developing economies. These nations vary significantly in their energy structures, industrial activities, environmental policies, and climate vulnerabilities. The three metrics— CO₂ emissions per capita, PM2.5 air pollution exposure, and renewable energy share in total consumption— were selected due to their relevance to key UN Sustainable Development Goals (SDGs 3, 7, and 13) and their interconnected impacts on environmental and human health. 

To guide our analysis, we propose the following research questions: 

1) What is the relationship between renewable energy adoption and CO₂ emissions across countries and over time? 

2) Are there observable correlations between CO₂ emissions and PM2.5 pollution exposure? 

3) Which countries demonstrate best practices or policy approaches that may serve as models for others in addressing these environmental challenges? 


\newpage

# Dataset Information
The data for this project were collected from the World Bank Databank, specifically from the World Development Indicators (WDI) dataset. These indicators are sourced from officially recognized international organizations and represent some of the most comprehensive and reliable global development data available. The WDI aggregates national, regional, and global statistics on topics related to environmental sustainability, public health, and economic growth. 

The final dataset includes annual values for the following four countries: United States, Germany, China, and Colombia, covering four key indicators: (1) CO₂ Emissions (metric tons per capita), (2) Renewable Energy Consumption (% of total final energy consumption), and (3) PM2.5 Pollution Exposure (mean annual exposure in µg/m³). 

These indicators were selected for their direct relevance to SDG 3 (Good Health and Well-being), SDG 7 (Affordable and Clean Energy), and SDG 13 (Climate Action). Together, these variables form the foundation for analyzing how environmental and energy infrastructure development correlate with greenhouse gas emissions. 

By leveraging this dataset, this project can investigate the relationship between CO₂ emissions and two environmental and public health variables—renewable energy consumption, and PM2.5 air pollution across two developed countries (Germany and the United States) and two developing countries (China and Colombia). The goal is to understand whether higher renewable energy adoption, cleaner air, and improved access to clean fuels are associated with lower carbon emissions in these national contexts from 2010 to 2020. 

Table: Dataset Structure Summary

Variable  | Description
------------: | :-------------
Country Name  | Name of the Country
Country Code  | Three-letter Country Code
Series Name  | Indicator Name
Year (2010-2020)  | Values for the respective indicator for each year


\newpage
# Dataset Wrangling
Data preparation was carried out using the R programming language, with heavy use of the tidyverse, dplyr, and readxl packages. The data wrangling process involved importing the original World Bank Excel dataset for each of the three variables of four countries using readxl::read_excel(). Unnecessary rows were removed, and missing values were replaced with "N/A" using the na.omit() function and the na_if() function. Then, the year column was converted to a character variable to facilitate data analysis. The dataset was then reshaped to a single panel structure by consolidating year columns into a single "Year" column, reorganizing the corresponding values into a "Value" column, and maintaining key identifiers like "Country Code," "Country Name," and "Series Name" via the pivot_longer () function. Subsequently, the "Value" column was converted to a numeric variable to ensure it is a format suitable for analysis. Finally, the processed dataset was saved as an Excel file in the Processed_Data folder using the write_xlsx() function. In this way, the final dataset was reshaped into a tidy format (long or wide as needed) for visualization and statistical analysis. 


# Exploratory Analysis 
The following summary statistic table provides an overview of the three indicators from 2010 to 2020, as part of the data exploration.
```{r indicator.summary, echo=FALSE}
#Computing the mean, maximum value, minimum value, standard deviation, and the range for each indicator
Summary_Stats_Indicator <- Sus_Env_Processed %>%
  group_by(`Series Name`) %>%
  summarize(
    n_obs = n(),  
    mean = mean(Value, na.rm = TRUE),  
    max = max(Value, na.rm = TRUE),    
    min = min(Value, na.rm = TRUE),    
    sd = sd(Value, na.rm = TRUE),     
    range = max(Value, na.rm = TRUE) - min(Value, na.rm = TRUE) 
  )


#Use the `kable` function to produce the summary statistic table in markdown format
#Producing the table for the summary statistic for three indicators
knitr::kable(Summary_Stats_Indicator, caption = "Summary Statistics for CO2, PM, and Renew", col.names = c("Series Name", "Observations", "Mean", "Max", "Min", "SD", "Range") , digits = 2)

```

The following three summary statistic tables provide an overview of the three indicators for each country from 2010 to 2020, as part of the data exploration.
```{r indicator.summary.country, echo=FALSE}
##Creating separate datasets for three variables of interest
CO2 <- Sus_Env_Processed %>% 
  filter(`Series Name` == "CO2")
Renew <- Sus_Env_Processed %>% 
  filter(`Series Name` == "Renew")
PM <- Sus_Env_Processed %>% 
  filter(`Series Name` == "PM")

#CO₂ Emissions
##Computing the mean, maximum value, minimum value, standard deviation, and the range for CO₂ Emissions in each country
Summary_Stats_CO2 <- CO2 %>%
  group_by(`Country Name`) %>%
  summarize(
    n_obs = n(),  
    mean = mean(Value, na.rm = TRUE),  
    max = max(Value, na.rm = TRUE),    
    min = min(Value, na.rm = TRUE),    
    sd = sd(Value, na.rm = TRUE),     
    range = max(Value, na.rm = TRUE) - min(Value, na.rm = TRUE) 
  )

##Use the `kable` function to produce the summary statistic table in markdown format
##Producing the table for the summary statistic for CO₂ Emissions in each country
knitr::kable(Summary_Stats_CO2, caption = "Summary Statistics for CO₂ Emissions (metric tons per capita)", col.names = c("Country Name", "Observations", "Mean", "Max", "Min", "SD", "Range") , digits = 2)

#Renewable Energy Consumption
##Computing the mean, maximum value, minimum value, standard deviation, and the range for renewable energy consumption in each country
Summary_Stats_Renew <- Renew %>%
  group_by(`Country Name`) %>%
  summarize(
    n_obs = n(),  
    mean = mean(Value, na.rm = TRUE),  
    max = max(Value, na.rm = TRUE),    
    min = min(Value, na.rm = TRUE),    
    sd = sd(Value, na.rm = TRUE),     
    range = max(Value, na.rm = TRUE) - min(Value, na.rm = TRUE) 
  )

##Use the `kable` function to produce the summary statistic table in markdown format
##Producing the table for the summary statistic for renewable energy consumption in each country
knitr::kable(Summary_Stats_Renew, caption = "Summary Statistics for Renewable Energy Consumption (% of total final energy consumption)", col.names = c("Country Name", "Observations", "Mean", "Max", "Min", "SD", "Range") , digits = 2)


#PM2.5 Pollution Exposure
##Computing the mean, maximum value, minimum value, standard deviation, and the range for PM2.5 Pollution Exposure in each country
Summary_Stats_PM <- PM %>%
  group_by(`Country Name`) %>%
  summarize(
    n_obs = n(),  
    mean = mean(Value, na.rm = TRUE),  
    max = max(Value, na.rm = TRUE),    
    min = min(Value, na.rm = TRUE),    
    sd = sd(Value, na.rm = TRUE),     
    range = max(Value, na.rm = TRUE) - min(Value, na.rm = TRUE) 
  )

##Use the `kable` function to produce the summary statistic table in markdown format
##Producing the table for the summary statistic for PM2.5 Pollution Exposure in each country
knitr::kable(Summary_Stats_PM, caption = "Summary Statistics for PM2.5 Pollution Exposure (mean annual exposure in µg/m³)", col.names = c("Country Name", "Observations", "Mean", "Max", "Min", "SD", "Range") , digits = 2)

```

The exploratory analysis of CO₂ emissions, renewable energy usage, and PM2.5 exposure data involved initial visualizations of each indicator across four countries (United States, Germany, China, and Colombia) from 2010-2020. After preliminary graphs revealed scaling challenges due to wide variations between nations, the y-axis was adjusted to better display trends while preserving comparisons. Examining differences in each indicator's levels, trajectories, and volatility helped identify potential patterns worthy of deeper investigation in subsequent analysis. In this way, this section could examine how CO₂ emissions, renewable energy usage, and PM2.5 exposure have evolved from 2010 to 2020 in Germany, the United States, China, and Colombia. 

```{r normalized.CO₂ Emissions.country, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Normalized to 2010 values for comparison
CO2_normalized <- CO2 %>%
  group_by(`Country Code`) %>%
  mutate(Normalized = Value / first(Value))

CO2_normalized_graph <- ggplot(CO2_normalized, aes(x = Year, y = Normalized, color = `Country Code`, group = `Country Code`)) +
  geom_line(linewidth = 1) +
  scale_color_manual(values = c("CHN" = "red", "COL" = "darkgreen", 
                                "DEU" = "turquoise", "USA" = "purple"),
                     labels = c("China", "Colombia", "Germany", "USA")) +
  labs(title = "Normalized CO₂ Emissions  (2010 = 1.0)", 
       y = "Relative to 2010 Levels") +
  theme_minimal() +
  theme(legend.position = "bottom")
print (CO2_normalized_graph)


```

Between 2010 and 2020, Germany and the United States exhibited a downward trend in CO₂ emissions, whereas China showed an upward trend. Colombia experienced an increase in emissions from 2010 to 2016, followed by a decline in the subsequent years.
This normalized graph highlights that while absolute emissions varied greatly, throughout 2010 to 2020:
-   The U.S. achieved the largest relative reduction (-25%)
-   China's emissions grew the most (+22%)
-   Colombia remained stable (+0.08%)
-   Germany showed a moderate decline (-23%)


```{r normalized.Renewable Energy Consumption.country, echo=FALSE}
# Normalized to 2010 values for comparison
Renew_normalized <- Renew %>%
  group_by(`Country Code`) %>%
  mutate(Normalized = Value / first(Value))

Renew_normalized_graph <- ggplot(Renew_normalized, aes(x = Year, y = Normalized, color = `Country Code`, group = `Country Code`)) +
  geom_line(linewidth = 1) +
  scale_color_manual(values = c("CHN" = "red", "COL" = "darkgreen", 
                                "DEU" = "turquoise", "USA" = "purple"),
                     labels = c("China", "Colombia", "Germany", "USA")) +
  labs(title = "Normalized Renewable Energy Consumption (2010 = 1.0)", 
       y = "Relative to 2010 Levels") +
  theme_minimal() +
  theme(legend.position = "bottom")
print (Renew_normalized_graph)


```
From 2010 to 2020, China, Germany, and the United States all demonstrated a notable upward trend in renewable energy consumption, while Colombia exhibited a modest overall increase. 
This normalized graph highlights that while absolute renewable energy consumption level varied greatly:
-   Germany achieved the largest relative increase (+60%)
-   The U.S. achieved an evident relative increase, too (+50%)
-   China showed a moderate increase (+21%)
-   Colombia remained stable (+0.06%)


```{r normalized.PM2.5 Pollution Exposure.country, echo=FALSE}
# Normalized to 2010 values for comparison
PM_normalized <- PM %>%
  group_by(`Country Code`) %>%
  mutate(Normalized = Value / first(Value))

PM_normalized_graph <- ggplot(PM_normalized, aes(x = Year, y = Normalized, color = `Country Code`, group = `Country Code`)) +
  geom_line(linewidth = 1) +
  scale_color_manual(values = c("CHN" = "red", "COL" = "darkgreen", 
                                "DEU" = "turquoise", "USA" = "purple"),
                     labels = c("China", "Colombia", "Germany", "USA")) +
  labs(title = "Normalized PM2.5 Pollution Exposure (2010 = 1.0)", 
       y = "Relative to 2010 Levels") +
  theme_minimal() +
  theme(legend.position = "bottom")
print (PM_normalized_graph)


```

Between 2010 and 2020, all four countries exhibited a significant decline in PM2.5 pollution exposure, although China experienced an initial increase from 2010 to 2013.
This normalized graph highlights that while absolute PM2.5 pollution exposure level varied greatly:
-   Germany achieved the largest relative reduction (-27%)
-   The U.S. achieved evident relative reduction, too (-17%)
-   China and Colombia both showed a moderate reduction (-11% and -12%, respectively)

These preliminary visualizations suggest fundamentally different CO₂ emissions, renewable energy usage, and PM2.5 exposure trajectories across countries, which the subsequent analysis will examine in greater depth through correlation tests, statistical comparisons, and policy context.


\newpage

# Analysis
## Question 1: What is the relationship between renewable energy adoption and CO₂ emissions across countries and over time?
```{r RQ1.1, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
##Creating separate datasets regarding each variable of interest across four countries
###PM
PM_USA <- PM %>% 
  filter(`Country Code` == "USA")
PM_DEU <- PM %>% 
  filter(`Country Code` == "DEU")
PM_COL <- PM %>% 
  filter(`Country Code` == "COL")
PM_CHN <- PM %>% 
  filter(`Country Code` == "CHN")

###CO2
CO2_USA <- CO2 %>% 
  filter(`Country Code` == "USA")
CO2_DEU <- CO2 %>% 
  filter(`Country Code` == "DEU")
CO2_COL <- CO2 %>% 
  filter(`Country Code` == "COL")
CO2_CHN <- CO2 %>% 
  filter(`Country Code` == "CHN")

###Renew
Renew_USA <- Renew %>% 
  filter(`Country Code` == "USA")
Renew_DEU <- Renew %>% 
  filter(`Country Code` == "DEU")
Renew_COL <- Renew %>% 
  filter(`Country Code` == "COL")
Renew_CHN <- Renew %>% 
  filter(`Country Code` == "CHN")


#cross country comparison for renewable energy
# Find the max and min Index values
max_index <- which.max(Renew$Index)
min_index <- which.min(Renew$Index)

# Create separate annotation data with nudging
label_data <- Renew[c(max_index, min_index), ]
label_data$nudge_y <- c(-0.2, 0.5)     # Adjust label position: max down, min up
label_data$vjust   <- c(1.5, -0.5)

# Plot the line graph
ggplot(Renew, aes(x = Year, y = Index, group = `Country Code`, color = `Country Code`)) +
  geom_line(size = 1.5) +
  geom_text(data = label_data[1, ], aes(label = Index), 
            vjust = label_data$vjust[1], nudge_y = label_data$nudge_y[1], size = 4) +
  geom_text(data = label_data[2, ], aes(label = Index), 
            vjust = label_data$vjust[2], nudge_y = label_data$nudge_y[2], size = 4) +
  labs(
    title = "Cross Country Comparison of Renewable Energy Trends", 
    x = "Year", 
    y = "% of Energy Consumption"
  ) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.title = element_blank()) +
  scale_y_continuous(expand = expansion(mult = c(0.1, 0.1))) +  # Add space above and below
  coord_cartesian(clip = "off")  # Prevent labels from being clipped

```
Overview of Renewable Energy Consumption
The widespread adoption of renewable energy is essential to mitigating the impacts of climate change caused by human activity. Renewable energy sources, such as solar, wind, geothermal, and hydropower, hold the potential to transform global energy systems, particularly by providing electricity to the **760 million people** who currently lack access to it. Additionally, replacing fossil fuels like coal, oil, and natural gas with renewable energy is crucial for reducing greenhouse gas emissions.
Although countries worldwide have made some progress in adopting renewable energy, the pace remains insufficient. In 2020, renewables accounted for just '12.6% of global energy consumption'. This rate of adoption is far from adequate to meet climate targets. To effectively limit global warming, it is necessary to 'triple renewable energy capacity by 2030'. Our analysis reveals that some nations have made more significant strides toward achieving this goal than others.
The World Bank tracks renewable energy use as a percentage of total energy consumption. In 2020, the average renewable energy share across the four countries in our study was **16.88%**. Among these countries, **Colombia** stands out as a leader, reaching a peak of **32% renewable energy** in 2017. **Germany** follows, with impressive but still insufficient renewable energy adoption compared to Colombia. In stark contrast, **the United States** has been much slower to transition to renewables, with a peak share of just **11% in 2020**, indicating substantial underperformance relative to global needs.

```{r RQ1.2, echo=FALSE}
# Calculate the correlation between Renewable and CO2
correlationCO2COL <- cor(CO2_COL$Index, RenewCOL$Index, method = "pearson")
print(correlationCOL)
correlationCO2CHN <- cor(CO2_COL$Index, RenewCHN$Index, method = "pearson")
print(correlationCHN)
correlationCO2USA <- cor(CO2_COL$Index, RenewUSA$Index, method = "pearson")
print(correlationCO2USA)
correlationCO2DEU <- cor(CO2_COL$Index, RenewDEU$Index, method = "pearson")
print(correlationDEU)
```
The correlation analysis reveals no universal relationship between renewable energy adoption and CO₂ emissions. While China shows a slight negative trend (-0.15), other countries (Colombia, USA, Germany) exhibit positive or neutral correlations, suggesting renewables alone are insufficient to cut emissions without explicit fossil fuel phase-outs. This underscores that national context—energy mix, policy, and economic growth—drives whether renewables effectively mitigate CO₂.



## Question 2: Are there observable correlations between CO₂ emissions and PM2.5 pollution exposure?

```{r RQ2.1, echo=FALSE}
# Round Index values to 2 decimal places
PM$Index <- round(PM$Index, 2)

# Re-run plotting code
ggplot(PM, aes(x = Year, y = Index, group = `Country Code`, color = `Country Code`)) +
  geom_line(size = 1.5) +
  labs(title = "Cross Country Comparison of PM2.5 Air Pollution", 
       x = "Year", y = "PM2.5 (µg/m³)") +
  geom_text(
    data = PM[c(max_index, min_index), ],
    aes(label = Index),  # Now shows 2 decimal places
    vjust = -0.5, hjust = 0.8, size = 4,
    nudge_x = 0.1, nudge_y = 0.1
  ) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5), legend.title = element_blank())

```
Overview of PM2.5
The proportion of a nation's population exposed to ambient PM2.5 concentrations above the WHO's recommended threshold of 10 μg/m³ serves as a critical indicator of air quality-related health risks. These fine particulate pollutants, primarily generated through combustion processes including vehicular emissions, industrial operations, and residential heating, demonstrate well-established dose-response relationships with adverse health outcomes. Epidemiological research confirms both acute effects such as increased hospitalizations for cardiorespiratory conditions and emergency room visits, as well as chronic consequences including reduced pulmonary function and elevated cardiovascular disease risk, with particular severity among pediatric and geriatric populations.

Our cross-national comparison reveals pronounced disparities in exposure levels, with China exhibiting systematically higher PM2.5 concentrations than the United States, Germany, and Colombia. This pattern likely reflects China's unique combination of coal-dependent energy infrastructure (accounting for approximately 60% of primary energy consumption), rapid industrial expansion during the 2000-2020 period averaging 8% annual GDP growth, and meteorological conditions prone to atmospheric stagnation. The United States demonstrates measurable improvements post-2010 attributable to Clean Air Act enforcement and fuel switching initiatives, while Germany maintains stable reductions despite complexities in its energy transition. Colombia's comparatively favorable profile correlates with its hydroelectric-dominated energy matrix, where renewables constitute over 70% of generation capacity.

These findings underscore the effectiveness of integrated policy approaches combining emission controls, energy infrastructure modernization, and urban planning interventions. The China-United States divergence particularly highlights the health benefits achievable through rigorous power plant emission standards, vehicle fleet renewal programs, and comprehensive air quality monitoring systems. Future research directions should prioritize quantitative health impact assessments using WHO-recommended methodologies, detailed source apportionment studies to identify sector-specific contributions, and longitudinal evaluations of intervention effectiveness, such as China's recent "Blue Sky" policy initiatives.

```{r RQ2.2, echo=FALSE}
# Calculate Pearson correlations (linear relationship strength):
correlationPMCOL <- cor(CO2_COL$Index, PMCOL$Index, 
                     method = "pearson", use = "complete.obs")  # Colombia
correlationPMCHN <- cor(CO2_CHN$Index, PMCHN$Index, 
                     method = "pearson", use = "complete.obs")  # China
correlationPMUSA <- cor(CO2_USA$Index, PMUSA$Index,  # Corrected from USACOL to PMUSA
                     method = "pearson", use = "complete.obs")  # USA
correlationPMDEU <- cor(CO2_DEU$Index, PMDEU$Index, 
                     method = "pearson", use = "complete.obs")  # Germany
print(correlationPMCOL)
print(correlationPMCHN)
print(correlationPMUSA)
print(correlationPMDEU)

```
While observable correlations exist, their strength and direction vary significantly by national context. This underscores the need for country-specific air quality management strategies that account for local emission source profiles and development pathways. The strong US correlation suggests co-control benefits from decarbonization, whereas China/Colombia's results indicate PM2.5 reduction may require additional targeted measures beyond CO₂ mitigation.


## Question 3: Which countries demonstrate best practices or policy approaches that may serve as models for others in addressing these environmental challenges?

The analysis reveals distinct yet complementary policy approaches that countries can emulate to address interconnected environmental challenges. Colombia stands out as a renewable energy leader, achieving 32% renewable energy consumption through strategic harnessing of its natural resources. The country's success stems from innovative policies like the Energy Transition Law, which created tax incentives for renewable projects, and robust public-private partnerships exemplified by Ecopetrol's investments. Colombia's National Energy Plan demonstrates how developing nations can leverage geographic advantages - in this case, hydropower and bioenergy resources - to build sustainable energy systems. The planned expansion into wind and solar energy through competitive auctions in the Guajira region offers a replicable model for resource-rich developing countries.

The United States provides critical lessons in air quality management, maintaining the lowest PM2.5 levels among the studied nations. This achievement primarily results from decades of stringent regulation under the Clean Air Act and its amendments, which imposed strict emissions caps on industries and vehicles. While the correlation between CO2 and PM2.5 reductions appears statistically weak, the U.S. experience shows how fuel switching and efficiency improvements can create valuable co-benefits for both climate and public health. America's regulatory framework offers a template for urbanizing nations struggling with particulate pollution, proving that emissions reductions aren't strictly prerequisite for air quality gains.

Germany exemplifies comprehensive decarbonization, successfully reducing CO2 emissions by 14% while cutting PM2.5 exposure by nearly 30%. This dual achievement stems from Germany's integrated policy approach, combining aggressive renewable energy subsidies with a structured coal phaseout plan and meaningful carbon pricing (€25-30/ton). The German model demonstrates how developed economies can orchestrate just transitions through policy sequencing - first building renewable capacity, then retiring fossil assets - while maintaining energy security. This approach has created measurable climate and health benefits, making it particularly relevant for industrialized nations.

China's experience, while highlighting the challenges of coal dependence, also shows promising policy innovations. The "Blue Sky" initiative reduced PM2.5 concentrations by 11% through stringent industrial emission standards and pilot carbon trading schemes. For coal-reliant developing economies, China's approach suggests that targeted industrial policies and gradual market mechanisms can achieve meaningful improvements even before full energy transitions are feasible. Each country's experience contributes unique insights to a global toolkit for sustainable development, emphasizing that effective solutions must be tailored to national circumstances while drawing on cross-border lessons. The collective experience underscores that environmental progress requires policy packages combining regulation, incentives, and innovation, adapted to each nation's resources and development stage.

\newpage

# Summary and Conclusions


\newpage

# References
<add references here if relevant, otherwise delete this section> 
